Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-09-05 ms.tex
discussion (S5.1) is added

>>>>

\memoYF{Need to elaborate. References are needed. }

For now, it is difficult to detect planetary-mass companions around low-mass evolved stars through other means. The major difficulty in radial velocity measurement is the stellar pulsation (rms of $>30m/s$ for K giants). If the orbital period is long enough compared to the period of pulsation, it is possible to average out the pulsation and detect radial velocity of planetary component, but this requires long period monitoring. For transit observation Pulsation also contributes to the noise in detecting transit signals \memoYF{?} and besides the transit signals would be as low as 1ppm. Due to the great luminosity of the host star, direct imaging is also difficult \memoYF{?}. Thus, for the time being, one would have to aim at discovering planetary companions around evolved stars, rather than targeting at known planetary systems.

Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
As mentioned in \S\ref{ss:timevariability}, auroral radio emission varies in association with several physical processes. In turn, radio emission could provide a unique pathway to get an idea of spin rotation period. (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars.) 
%
Also, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets.

Obviously, if the spectra could be obtained and the frequency cut-off is detected, it tells us the magnetic field strengths of the planetary surface. 
Such information would be most useful if we could follow up the system by radial velocity to get constraints on the planetary mass, because with such information, we can contest the scaling laws of planetary magnetic field strength as a function of mass.
